On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-09-26 Manuscript/manuscript.tex
Updated table

\begin{table}
  \centering
  \caption{2019 vs 2022 compares data from the same athletes who competed at the
  2019 and 2022 World Track and Field Championships. 2022 vs 2023 compares data
  from the same athletes who competed at the 2022 and 2023 World Track and Field
  Championships. Nat vs Inter compares data from the same athletes who competed
  at the 2022 national-level championships and the 2022 World Track and Field
  Championships.}
  \begin{tabular}{c c c c c} 
   \toprule
   Comparison & Permutation & Asymptotic \\ 
   \midrule
   2019 vs 2022 & $2.9\cdot10^{-3}$ & $2.3\cdot10^{-2}$ \\
   2022 vs 2023 & $3.0\cdot10^{-3}$ & $1.0\cdot10^{-2}$ \\
   2022 National vs International & $2.2\cdot10^{-16}$ & $1.0\cdot10^{-3}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Clusrankresults}
\end{table}

Table~\ref{tab:Clusrankresults} shows the results generated from both the 
permutation (exact) and asymptotic rank-based tests for the three comparisons, 
as discussed previously in Section~\ref{sec:rank}.    
The national versus international comparison
produced lower p-values than the 2019 versus 2022 comparison, with the
national vs international permutation test producing a p-value of 
$2.2\cdot10^{-16}$, which is the smallest possible value achievable in R.  
\eds{Prof. Yan, is this possible based on 1000 permutations?}
\jy{That cannot be true.  Redo with a much bigger number of permutations and
  update the table.}
This
is a highly significant test result and shows that athletes who competed at the
2022 World Track and Field Championships were on average, significantly faster
at reacting than they were just a few months prior.  For the 2019 versus 2022
same athlete comparison with permutation test, the p-value was 
$2.9\cdot10^{-3}$, which is significant at $\alpha = 0.01$.  The result of
comparing 2022 and 2023 was very similar to the above result, as the p-value
from the permutation test was $3.0\cdot10^{-3}$.  Taken together, these three
tests help show that athletes competing at the 2022 World Track and Field
Championships had faster reaction times than when they had competed previously.

>>>>

\begin{table}
  \centering
  \caption{2019 vs 2022 compares data from the same athletes who competed at the
  2019 and 2022 World Track and Field Championships. 2022 vs 2023 compares data
  from the same athletes who competed at the 2022 and 2023 World Track and Field
  Championships. Nat vs Inter compares data from the same athletes who competed
  at the 2022 national-level championships and the 2022 World Track and Field
  Championships.}
  \begin{tabular}{c c c c c} 
   \toprule
   Comparison & Permutation & Asymptotic \\ 
   \midrule
   2019 vs 2022 & $2.8\cdot10^{-2}$ & $2.9\cdot10^{-3}$ \\
   2022 vs 2023 & $1.1\cdot10^{-2}$ & $3.1\cdot10^{-3}$ \\
   2022 National vs International & $2\cdot10^{-6}$ & $1.1\cdot10^{-3}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Clusrankresults}
\end{table}

Table~\ref{tab:Clusrankresults} shows the results generated from both the 
permutation (exact) and asymptotic rank-based tests for the three comparisons, 
as discussed previously in Section~\ref{sec:rank}.    
The national versus international comparison
produced lower p-values than the 2019 versus 2022 comparison, with the
national vs international permutation test producing a p-value of 
$2.2\cdot10^{-16}$, which is the smallest possible value achievable in R.  
\eds{Prof. Yan, is this possible based on 1000 permutations?}
\jy{That cannot be true.  Redo with a much bigger number of permutations and
  update the table.}
\of{Done, permutation results were for B = 1 million}
This
is a highly significant test result and shows that athletes who competed at the
2022 World Track and Field Championships were on average, significantly faster
at reacting than they were just a few months prior.  For the 2019 versus 2022
same athlete comparison with permutation test, the p-value was 
$2.9\cdot10^{-3}$, which is significant at $\alpha = 0.01$.  The result of
comparing 2022 and 2023 was very similar to the above result, as the p-value
from the permutation test was $3.0\cdot10^{-3}$.  Taken together, these three
tests help show that athletes competing at the 2022 World Track and Field
Championships had faster reaction times than when they had competed previously.
